A survey of HTTP caching options on the open Web

### 2015-01-02 sanity/paper1.tex
minor
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@913 43ef1190-90fd-4dd7-a769-d0121f02b80e
comment on the removal of eresponse
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@925 43ef1190-90fd-4dd7-a769-d0121f02b80e

This results in an NQuads file per host, which is then loaded into a
SPARQL Endpoint\todo{which} for analysis by using the statistics
system R.

@@

For resource types other than ``vocabulary'', we look for SPARQL
endpoints in the response, using the predicates \rdfterm{sd:endpoint}
and \rdfterm{void:sparqlEndpoint}. We then do the same query as above
and record the relevant headers.

>>>>

This results in an NQuads file per host, which is then loaded into a
SPARQL Endpoint\todo{which} for analysis by using the statistics
system R\todo{ref}.

@@

For resource types other than ``vocabulary'', we look for SPARQL
endpoints in the response, using the predicates \rdfterm{sd:endpoint}
and \rdfterm{void:sparqlEndpoint}. We then do the same query as above
and record the relevant headers. Unfortunately, we found early that
this only turns up misconfigured endpoints that point to localhost,
and was removed from the spider for the final analysis.
